{ Das CrypTool-Skript: \\ Kryptographie, Mathematik und mehr} \\ \vspace{30pt} {\large Hintergrundmaterial und Zusatzinformationen\\%*[-8pt] zum freien E-Learning-Programm CrypTool\\ (9. Auflage -- zu Version 1.4.20)} \vspace{60pt}

### 2009-08-05 script/de/chapters/primes.tex
reduced number of pdfTeX warnings (hyperlink related) from 615 to 15; moved index{...} out of headings

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Carmichaelzahlen\index{Zahlen!Carmichaelzahl}}
Wie \hyperlink{HT-Carmichael-number01}{oben} in
Kapitel~\ref{L-Carmichael-number01} erwähnt,
sind nicht alle Carmichaelzahlen prim.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Pseudoprimzahlen%
\index{Primzahl!Pseudoprimzahl}\index{Zahlen!Pseudoprimzahl}%
}
Siehe \hyperlink{HT-Pseudoprimenumber01}{oben} in
Kapitel~\ref{L-Pseudoprimenumber01}.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Starke Pseudoprimzahlen%
\index{Primzahl!starke Pseudoprimzahlen} \index{Zahlen!starke Pseudoprimzahl}%
}
Siehe \hyperlink{HT-Strongpseudoprimenumber01}{oben} in
Kapitel~\ref{L-Strongpseudoprimenumber01}.

@@

%----------------------------------------
\index{Eratosthenes!Sieb}
\paragraph{Sieb des Eratosthenes\index{Eratosthenes!Sieb}}\mbox{}
\hypertarget{SieveEratosthenes01}{}

>>>>

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Carmichaelzahlen}\index{Zahlen!Carmichaelzahl}
Wie \hyperlink{HT-Carmichael-number01}{oben} in
Kapitel~\ref{L-Carmichael-number01} erwähnt,
sind nicht alle Carmichaelzahlen prim.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Pseudoprimzahlen}
\index{Primzahl!Pseudoprimzahl}\index{Zahlen!Pseudoprimzahl}
Siehe \hyperlink{HT-Pseudoprimenumber01}{oben} in
Kapitel~\ref{L-Pseudoprimenumber01}.

% --------------------------------------------------------------------------
\vskip +10 pt
\subsection{Starke Pseudoprimzahlen}
\index{Primzahl!starke Pseudoprimzahlen} \index{Zahlen!starke Pseudoprimzahl}
Siehe \hyperlink{HT-Strongpseudoprimenumber01}{oben} in
Kapitel~\ref{L-Strongpseudoprimenumber01}.

@@

%----------------------------------------
\index{Eratosthenes!Sieb}
\paragraph{Sieb des Eratosthenes}\index{Eratosthenes!Sieb}\mbox{}
\hypertarget{SieveEratosthenes01}{}

### 2009-08-05 script/de/script-de.tex
added argument to example and remark definitions
fixed various table to use the table environment and caption
CT script: added new cover page (de+en); chap 4: appendix with sage samples: changed the name of some self-defined functions... - not finished yet (en only)
reduced number of pdfTeX warnings (hyperlink related) from 615 to 15; moved index{...} out of headings

\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
% \usepackage{flafter} Versuch von Hrn. Koy, zu erzwingen, dass 
%     Grafiken/Verschiebbare Objekte (floats) immer an der Stelle eingefügt
%     werden, wo sie aufgerufen werden. Tat nicht.

%\usepackage{myThanks}
%\usepackage{thumbpdf}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true]{hyperref}
%\usepackage[T1]{fontenc}
%\usepackage{times}
%\usepackage{pslatex}
%\usepackage{ae,aecompl}

% Formatierung der Fußnoten
\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage{url}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
\usepackage{float}
\floatstyle{ruled}
\newfloat{sagecode}{!h}{loc}[chapter]
\floatname{sagecode}{Sample}

@@

% \setlength{\textwidth}{460 pt}
% \hoffset-0.7in
\newtheorem{definition}{Definition}[section]
\newtheorem{satz}{Satz}[section]
\newenvironment{Beweis}[1]
  {\textbf{Beweis #1} \\}
  {\hfill$\Box$ \\}
\newenvironment{example}{\noindent\textbf{Beispiel.}}{}
\newenvironment{remark}{\noindent\textbf{Bemerkung.}}{}

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}   % SR_2009: added new cover

% \usepackage{flafter} Versuch von Hrn. Koy, zu erzwingen, dass 
%     Grafiken/Verschiebbare Objekte (floats) immer an der Stelle eingefügt
%     werden, wo sie aufgerufen werden. Tat nicht.

%\usepackage{myThanks}
%\usepackage{thumbpdf}
%\usepackage[T1]{fontenc}
%\usepackage{times}
%\usepackage{pslatex}
%\usepackage{ae,aecompl}

% Formatierung der Fußnoten
\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage{url}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
\usepackage{float}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,hypertexnames=false]{hyperref}
%To reduce the number of hyperlink related 'pdfTeX warning's we use options 
%pdfpagelabels and hypertexnames=false and place hyperref after float.
%Option debug helps finding problems.

\floatstyle{ruled}
\newfloat{sagecode}{!h}{loc}[chapter]
\floatname{sagecode}{Sage-Beispiel}

@@

% \setlength{\textwidth}{460 pt}
% \hoffset-0.7in
\newtheorem{definition}{Definition}[section]
\newtheorem{satz}{Satz}[section]
\newenvironment{Beweis}[1]
  {\textbf{Beweis #1} \\}
  {\hfill$\Box$ \\}
\newenvironment{example}[1]{\noindent\textbf{Beispiel#1}}{}
\newenvironment{remark}[1]{\noindent\textbf{Bemerkung#1}}{}

@@

\includepdf[page=1]{figures/coverv1_de.pdf}    % SR_2009: added new cover
